Structures Report

### 2017-03-15 mu/structures-report/structures-report.tex
Report almost finished. Need fix minimal issues.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AB %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ab} % (fold)
\label{sec:ab}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% xb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\mathcal{V}^{\mathrm{xb}} $}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvxb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{xb}} $ is for 
    155$^{\circ}$.}
    \label{fig:ab-magvxbincang}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxx.pdf}
    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxy.pdf}\\
    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vxz.pdf}
    \caption{Cheking angle of incidence for $xb$ components. There is a
    different angle for each component to have the most intense response.}
    \label{fig:ab-xbangcomp}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvxb.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ for different
    polarization angles.}
    \label{fig:ab-magvxb}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 155$^{\circ}$.}
    \label{fig:ab-vxb}
\end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%% yb [0.5:3.0] %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$\mathcal{V}^{\mathrm{yb}} $}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvyb-incang-4545.pdf}
    \caption{The most intense response for $\mathcal{V}^{\mathrm{yb}} $ is for 
    155$^{\circ}$.}
    \label{fig:ab-magvybincang}
\end{figure}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vyx.pdf}
    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vyy.pdf}\\
    \includegraphics[width=0.45\textwidth]{abplots/hnbGh-ab-vyz.pdf}
    \caption{Cheking angle of incidence for $yb$ components. There is a
    different angle for each component to have the most intense response.}
    \label{fig:ab-ybangcomp}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvyb.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{yb}}|$ for different
    polarization angles.}
    \label{fig:ab-magvyb}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vyb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{yb}} $ @ 125$^{\circ}$.}
    \label{fig:ab-vyb}
\end{figure}

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.5:3.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vxb-rtp.pdf}
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vyb-rtp.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:ab-rtp}
\end{figure}

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyx-layers.pdf}
%     \caption{Layer decomposition for the most intense response:
%     $\mathcal{V}^{\mathrm{yz}}$.}
%     \label{fig:aa-lay}
% \end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vab-comp.pdf}
    \caption{Comparisson of the most intense response vs the most intense
    responses of CdSe and GaAs.}
    \label{fig:ab-comp}
\end{figure}

% section ab (end)
